---
title: "Scott Creek WY2019 Microplastics Study"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Scott Lagoon 2018 DTS Study (AKO analysis notes)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  github_document:
    toc: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "readme-figs/"
)
```


## General Goals

Microplastics (MP; plastic particles < 5 mm in diameter) are a growing environmental concern which threatens the health of aquatic ecosystems worldwide. Recent research has documented the ubiquitous nature of MP in the marine environment and the assimilation of MP in fishes at all trophic levels. Comparatively little is known, however, about the occurrence and concentration of MP in riverine ecosystems. The project goal is to determine if MP is present in the Scott Creek basin. Our methods include sampling suspended MP in the water column and documenting the occurrence of MP in the stomachs of juvenile steelhead *(Oncorhynchus mykiss)*. This project is an important first step in identifying the presence of MP in coastal watersheds and is a starting point for assessing potential impacts on riverine fishes.


      
**Description of Datasets:**  
TBD